A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-03 03_Prep_data.Rmd
correction

Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m2`.
We will retain dose as a variable inside the `trial` factor.

>>>>

Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m1`.
We will retain dose as a variable inside the `trial` factor.
